A Modular Framework for Developing, Deploying, and Evaluating Game-Theoretic Strategy Design Exercises

### 2018-05-07 paper.tex
Start biber

@@

@@

\section*{Implementation}
% TODO: signposting
% TODO: make it fit
Before the first problem set of the course was assigned in this semester, Professor Weinberg and I designed a handout interface and tools to allow students to test their strategies against each other, which I then implemented.
The game simulates college admissions using stable matchings.
While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.~\cite{Kernighan and Pike chapter 4}
I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.

@@

However, because of conscious design decisions to factor out repeated code from assignment implementations, my implementation has accomplished what previous implementations had not.
It is modular, as described above, so that new extensions such as additional tools or interfaces can be written for strategy design exercises.
Throughout the semester, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce such extensions.
It is reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.
% TODO redraw using Powerpoint
% TODO use this diagram when I talk about modularization earlier
\begin{figure}[hbt]
  \centering
  \includegraphics[width=0.75\linewidth]{Handwritten_Diagram.jpg}
  \caption{TODO: This is a gray image.}\label{fig:gray}
\end{figure}

@@

    // Let you know if you won, and how much the winners paid
    // Called once per day after the auction
    public void addResults(List<Double> bids, int myBid, double myPayment);
}
\end{minted}
  \caption{\texttt{interface Bidder} demonstrates a strategy interface}\label{minted:Bidder}
\end{figure}
This interface describes the necessary functions of a student strategy for the auctions exercise.
Each day, they must bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results'') and assign different values to words auctioned on different days.
The strategy also has access the winning bids for each of the ten sponsored results from each past day and knows which of those bids were its own.\footnote{When a strategy wins, it is also told how much it paid.}
This allows the strategy to obey the budget constraint: across all 1000 days, it may not spend more than 500.
These constants are not documented in the interface as designed, only in the assignment specification.
The instructors distribute a simple sample student implementation --- in this case, the truthful bidder.
Zhang also implemented a program used to grade the student-submitted strategies which consisted of two methods: \texttt{main} and \texttt{trial}.
The former ran 100 trials and printed out the results, averaging the outcomes across each trial for each student.
The latter contained an implementation of the generalized second-price auction format described in the assignment specification.

@@

Given a CSV file as input with the header row \texttt{netID} and a row for each student's name, the following function is thereby rewritten to instantiate one implementation of each Student class listed in the configuration file:
\begin{figure}[hbt]
\begin{minted}{java}
    // S, T, W are simulation parameters documented in the student interface
    public static int[] oneEachTrial(double S, double T, double W)
    {
        // Initialize students
        Student[] students = new Student[N];
        //R students[{0}] = new Student_{netID}();//
        return runTrial(students, S, T, W);
    }
\end{minted}
  \caption{\texttt{oneEachTrial} demonstrates usage of \texttt{formatBase.py}}\label{minted:oneEachTrial}
\end{figure}

My modular design allows for data collection code to vary without additional overhead.
The following method instantiates an instance of an instructor-provided strategy using reflection, in addition to the strategies specified in the configuration file.
This method is useful for grading assignments.
\begin{figure}[hbt]
\begin{minted}{java}
    public static <Student_T extends Student> int[] withExtraTrial(
            Class<Student_T> clazz, double S, double T, double W)
    {
        // Initialize students
        Student[] students = new Student[N+1];
        //R students[{0}] = new Student_{netID}();//
        try {
            students[N] = clazz.getConstructor().newInstance();
        } catch (ReflectiveOperationException roe) {
            roe.printStackTrace();
            System.exit(1);
        }

@@

In summary, as described in Figuree~\ref{figure:outline}, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that post-process the results of those trials to provide low-latency feedback or for auto-grading, and automating these steps with a Makefile to configure, compile, and run the assignment simulation.

@@

% Thus, quantitative metrics, including software failure rates and instructor time usage, and qualitative metrics, including student and instructor satisfaction, both illustrate the improvements to the course and emphasize the importance of quality tooling to quality programming-based assignments.

% What are your thoughts on how well the strategy design exercises have gone this year? Specifically, I'm interested in your satisfaction with the implementations and software, and the amount of instructor time and frustration spent. (And less intersted in comments on the course policy decisions that may have impacted how well they went, sicne that's not in the scope of my independent work.)

@@

>>>>

\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{biblatex}

@@

\addbibresource{references.bib}

@@

\section*{Implementation}
Before the first problem set of the course was assigned in this semester, Professor Weinberg and I designed a handout interface and tools to allow students to test their strategies against each other, which I then implemented.
The game simulates college admissions using stable matchings.
While I implemented this handout with the explicit goal of producing a tool to test out multiple different student strategies in the specified application environment, I followed the principles of modular software design taught in COS 217.~\cite{Kernighan and Pike chapter 4}
I factored out the code which implemented the Gale-Shapley deferred acceptance algorithm for stable matchings from the code which performed randomized trials of the stable matchings and produced performance statistics for students.

@@

However, because of conscious design decisions to factor out repeated code within each assignment, my project will be more reusable than implementations from past semesters.
It is also extensible, so new extensions such as additional tools or interfaces can be written for strategy design exercises.
The structure of my project is outlined in Figure~\ref{fig:outline}.
The modular layout ensures that each component can be designated as either reusable between assignments (green), written for each assignment by the instructors (blue), or submitted by each student for each assignment (orange).
Throughout the semester, I have leveraged my role as an undergraduate course assistant for COS 445 during the current semester in order to identify and produce extensions, including CS Dropbox ``Check Submit'' functionality and a student strategy leaderboard.
This framework reusable, both for the same assignments in future years and for new strategy design exercises implemented by future course staff with lower overhead.

\begin{figure}[hbt]
  \centering
  \includegraphics[scale=0.75]{outline.png}
  \caption{The implementation structure of my framework.}\label{fig:outline}
\end{figure}

@@

    // Let you know if you won, and how much the winners paid
    // Called once per day after the auction
    public void addResults(List<Double> bids, int myBid, double myPayment);
}
\end{minted}
  \caption{\texttt{interface Bidder} demonstrates a strategy interface}\label{minted:Bidder}
\end{figure}

This interface describes the necessary functions of a student strategy for the auctions exercise.
Each day, they must bid on an auction of advertising slots which appear on a search results page (often called ``sponsored search results'') and assign different values to words auctioned on different days.
The strategy also has access the winning bids for each of the ten sponsored results from each past day and knows which of those bids were its own.\footnote{When a strategy wins, it is also told how much it paid.}
This allows the strategy to obey the budget constraint: across all 1000 days, it may not spend more than 500.
These constants are not documented in the interface as designed, only in the assignment specification.
The instructors distribute a simple sample student implementation --- in this case, the truthful bidder.
Zhang also implemented a program used to grade the student-submitted strategies which consisted of two methods: \texttt{main} and \texttt{trial}.
The former ran 100 trials and printed out the results, averaging the outcomes across each trial for each student.
The latter contained an implementation of the generalized second-price auction format described in the assignment specification.

@@

Given a CSV file as input with the header row \texttt{netID} and a row for each student's name, the method in Figure~\ref{minted:oneEachTrial} will be rewritten to instantiate one object of each Student implementation listed in the configuration file:
\begin{figure}[hbt]
\begin{minted}{java}
    // S, T, W are simulation parameters documented in the student interface
    public static int[] oneEachTrial(double S, double T, double W)
    {
        // Initialize students
        Student[] students = new Student[N];
        //R students[{0}] = new Student_{netID}();//
        return runTrial(students, S, T, W);
    }
\end{minted}
  \caption{\texttt{oneEachTrial} demonstrates usage of \texttt{formatBase.py}}\label{minted:oneEachTrial}
\end{figure}
My modular design allows for data collection code to vary without additional overhead.
This is shown in Figure~\ref{minted:withExtraTrial}, which instantiates an instructor-provided strategy using reflection, in addition to the strategies specified in the configuration file.
This method is useful for grading assignments.
\begin{figure}[hbt]
\begin{minted}{java}
    public static <Student_T extends Student> int[] withExtraTrial(
            Class<Student_T> clazz, double S, double T, double W)
    {
        // Initialize students
        Student[] students = new Student[N+1];
        //R students[{0}] = new Student_{netID}();//
        try {
            students[N] = clazz.getConstructor().newInstance();
        } catch (ReflectiveOperationException roe) {
            roe.printStackTrace();
            System.exit(1);
        }

@@

In summary, as described in Figure~\ref{fig:outline}, each assignment consists of a strategy interface, implementations of that strategy, a list of those implementations, a \texttt{runTrial} method which specifies how to evaluate those strategies, methods which run specific subsets of strategies, methods that post-process the results of those trials to provide low-latency feedback or for auto-grading, and automating these steps with a Makefile to configure, compile, and run the assignment simulation.

@@

% What are your thoughts on how well the strategy design exercises have gone this year? Specifically, I'm interested in your satisfaction with the implementations and software, and the amount of instructor time and frustration spent.

@@

\bstctlcite{bstctl:etal, bstctl:nodash, bstctl:simpurl}
\medskip
\printbibliography[]
